Elders home characteristics/activity summary

### 2020-03-12 demographics_summary.Rmd
plot and summary updates

---
title: "EldersAIR: demographics summary"
author: "Ethan Walker"
date: "Started 6 March 2020, Updated 10 March 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
```

# Load individual datasets
```{r}
elders_ids_linked <- read_rds("Output/elders_ids_linked.rds")
elders_pm <- read_rds("Output/elders_pm_clean.rds")
```

##### For Winter 1, there were 145 homes with demographic data (76 NN and 69 NP)
##### and 150 participants with demographic data (79 NN and 71 NP)
##### 5 homes had 2 participants (3 NN and 2 NP); all other homes had 1 participant

# Filter for homes that have PM data
```{r}
demographics_filtered <- elders_ids_linked %>% 
  filter(winter_id == 1) %>% 
  filter(!is.na(gender)) 
```

# Summarize demographics data
```{r}
# Summarize numeric vars: total_residents, residents_under18, age_nov1
elders_dems <- demographics_filtered %>%  
  #group_by(area) %>% 
  summarize("Mean" = mean(age_nov1, na.rm = TRUE), 
            "SD" = sd(age_nov1, na.rm = TRUE),
            "min" = min(age_nov1, na.rm = TRUE), 
            "max" = max(age_nov1, na.rm = TRUE))
kable(elders_dems, digits = 1, align = "c")

>>>>

---
title: "EldersAIR: demographics summary"
author: "Ethan Walker"
date: "Started 6 March 2020, Updated 12 March 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
library(knitr)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```

```{r}
# Load individual datasets

elders_ids_linked <- read_rds("Output/elders_ids_linked.rds")
elders_pm <- read_rds("Output/elders_pm_clean.rds")
```

## For Winter 1, there were 145 homes with demographic data (76 NN and 69 NP)
## and 150 participants with demographic data (79 NN and 71 NP)
## 5 homes had 2 participants (3 NN and 2 NP); all other homes had 1 participant

```{r}
# Filter for Winter 1; remove NAs

demographics_filtered <- elders_ids_linked %>% 
  filter(winter_id == 1) %>% 
  filter(!is.na(gender)) %>% 
  mutate(income = factor(income,
                         levels = c("Less than $20,000", "$20,000 to $29,999",
                                    "$30,000 to $39,999", "$40,000 to $49,999",
                                    "$50,000 to $74,999", "$75,000 to $99,999",
                                    "$100,000 or more")),
         education = factor(education,
                            levels = c("Less than high school",
                                       "High school diploma or GED",
                                       "Some college",
                                       "College degree")))
```

```{r}
# Demographics summary stats function

demographics_function <- function(data, var, title_label, y_label) {

  demographics_plot <- data %>% 
  filter(winter_id == 1) %>% 
  select(area, var) %>% 
  rename(plot_var = var) %>% 
  filter(!is.na(plot_var)) %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    labs(title = title_label) +
    ylab(y_label) +
    scale_fill_manual(values = jv_palette)
  demographics_plot

}

demographics_function(demographics_filtered, "gender", "Participant sex", "count")
demographics_function(demographics_filtered, "hispanic", "Hispanic ethnicity", "count")
demographics_function(demographics_filtered, "race", "Participant race", "count")
demographics_function(demographics_filtered, "income", "Household income", "count")
demographics_function(demographics_filtered, "education", "Participant education", "count")
demographics_function(demographics_filtered, "total_residents", "Total residents", "count")
demographics_function(demographics_filtered, "residents_under18", "Residents under 18", "count")
```

```{r}
demo_summary_function <- function(data, var, title_label, y_label) {

  demo_summary <- data %>% 
    filter(winter_id == 1) %>% 
    #select(var) %>% 
    select(area, var) %>% 
    group_by(area) %>% 
    summarize_all(list(mean=mean, sd=sd, min=min, med=median, max=max), na.rm = TRUE)
  demo_summary <<- demo_summary

  demo_plot <- data %>% 
    filter(winter_id == 1) %>% 
    select(area, var) %>% 
    rename(plot_var = var) %>% 
    filter(!is.na(plot_var)) %>% 
    ggplot(aes(area, plot_var)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red",
                 position=position_nudge(x = -0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=mean, geom="text", 
                 size=7, position=position_nudge(x = -0.35, y = 0)) +
    stat_summary(fun.y=median, geom="point", shape=16, size=4, color="blue",
                 position=position_nudge(x = 0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=median, geom="text", 
                 size=7, position=position_nudge(x = 0.35, y = 0)) +
    theme_minimal() +
    labs(title = title_label, subtitle = "Mean = Red, Median = Blue") +
    ylab(y_label) +
    theme(title = element_text(size = 20, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) 
  demo_plot

}

demo_summary_function(demographics_filtered, "age_nov1", "Age, Nov 1", "years")
demo_summary_function(demographics_filtered, "total_residents", "Total residents", "count")
demo_summary_function(demographics_filtered, "residents_under18", "Residents under 18", "count")
```

```{r, include=FALSE}
# Summarize demographics data

# Summarize numeric vars: total_residents, residents_under18, age_nov1
elders_dems <- demographics_filtered %>%  
  #group_by(area) %>% 
  summarize("Mean" = mean(age_nov1, na.rm = TRUE), 
            "SD" = sd(age_nov1, na.rm = TRUE),
            "min" = min(age_nov1, na.rm = TRUE), 
            "max" = max(age_nov1, na.rm = TRUE))
kable(elders_dems, digits = 1, align = "c")

### 2020-03-12 health_history_summary.Rmd
plot and summary updates

---
title: "EldersAIR Health History Summary"
author: "Ethan Walker"
date: "Started 11 March 2020, Updated 11 March 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

# Load data
```{r}
elders_ids_linked <- read_rds("Output/elders_ids_linked.rds") %>% 
  filter(winter_id == 1 | winter_id == 2) %>% 
  arrange(area, adult_id_num)

@@

# Health history summary stats 
```{r}
health_hx_function <- function(data, var, title_label, y_label) {

  home_plot <- data %>% 
  filter(winter_id == 1) %>% 
  select(area, var) %>% 
  rename(plot_var = var) %>% 
  filter(!is.na(plot_var)) %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    labs(title = title_label) +
    ylab(y_label) +
    scale_fill_manual(values = jv_palette)
  home_plot

@@

health_hx_function(elders_health_hx, "rheum_arth", "Rheumatoid Arth", "count")
health_hx_function(elders_health_hx, "lupus", "Lupus", "count")
health_hx_function(elders_health_hx, "scleroderma", "Scleroderma", "count")
health_hx_function(elders_health_hx, "psoriasis", "Psoriasis", "count")
health_hx_function(elders_health_hx, "asthma", "Asthma", "count")
health_hx_function(elders_health_hx, "eczema", "Eczema", "count")
health_hx_function(elders_health_hx, "emphysema", "Emphysema", "count")
health_hx_function(elders_health_hx, "chronicbronchitis", "Chronic bronchitis", "count")
health_hx_function(elders_health_hx, "copd", "COPD", "count")
health_hx_function(elders_health_hx, "sarcoidosis", "Sarcoidosis", "count")
health_hx_function(elders_health_hx, "scleroderma", "Scleroderma", "count")
health_hx_function(elders_health_hx, "hayfever", "Hayfever", "count")
health_hx_function(elders_health_hx, "allergies", "Allergies", "count")
health_hx_function(elders_health_hx, "gerd", "GERD", "count")
health_hx_function(elders_health_hx, "chrohns", "Chrohns", "count")
health_hx_function(elders_health_hx, "colitis", "Colitis", "count")
health_hx_function(elders_health_hx, "sleepapnea", "Sleep apnea", "count")
health_hx_function(elders_health_hx, "kidneyfailure", "Kidney failure", "count")
health_hx_function(elders_health_hx, "pleuraleffusion", "Pleural effusion", "count")
health_hx_function(elders_health_hx, "pleurisy", "Pleurisy", "count")
health_hx_function(elders_health_hx, "pneumonia", "Pneumonia", "count")
health_hx_function(elders_health_hx, "pneumothorax", "Pneumothorax", "count")
health_hx_function(elders_health_hx, "empyema", "Empyema", "count")
health_hx_function(elders_health_hx, "brokenribs", "Broken ribs", "count")
health_hx_function(elders_health_hx, "coronaryarterydisease", "Coronary artery disease", "count")
health_hx_function(elders_health_hx, "angina", "Angina", "count")
health_hx_function(elders_health_hx, "heartattack", "Heart attack", "count")
health_hx_function(elders_health_hx, "chf", "CHF", "count")
health_hx_function(elders_health_hx, "abnormalhr", "Abnormal HR", "count")
health_hx_function(elders_health_hx, "pacemaker", "Pacemaker", "count")
health_hx_function(elders_health_hx, "icd", "Cardiac defibrillator", "count")
health_hx_function(elders_health_hx, "valvedisease", "Valve disease", "count")
health_hx_function(elders_health_hx, "hypertension", "Hypertension", "count")
health_hx_function(elders_health_hx, "circlegs", "Circulation problems in legs", "count")
health_hx_function(elders_health_hx, "circhead", "Circulation problems in head/neck", "count")
health_hx_function(elders_health_hx, "stroke", "Stroke", "count")
health_hx_function(elders_health_hx, "diabetes", "Diabetes", "count")
health_hx_function(elders_health_hx, "thyroiddisease", "Thyroid disease", "count")
health_hx_function(elders_health_hx, "anemia", "Anemia", "count")
health_hx_function(elders_health_hx, "cancer", "Cancer", "count")
health_hx_function(elders_health_hx, "tobusenow", "Tobacco use now", "count")
health_hx_function(elders_health_hx, "tobuseever", "Tobacco use ever", "count")
health_hx_function(elders_health_hx, "agefirst", "Age started smoking", "count")
health_hx_function(elders_health_hx, "agequit", "Age quit smoking", "count")
health_hx_function(elders_health_hx, "nowperday", "cigarettes per day now", "count")
health_hx_function(elders_health_hx, "aveperday", "Average smoked per day", "count")
health_hx_function(elders_health_hx, "peakperday", "Peak smoked per day", "count")
health_hx_function(elders_health_hx, "cigarspipes", "Current/past cigar/pipe use", "count")
```

# Health extra summary stats 
```{r}
health_hx_function <- function(data, var, title_label, y_label) {

  home_plot <- data %>% 
  filter(winter_id == 1) %>% 
  select(area, var) %>% 
  rename(plot_var = var) %>% 
  filter(!is.na(plot_var)) %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    labs(title = title_label) +
    ylab(y_label) +
    scale_fill_manual(values = jv_palette)
  home_plot

>>>>

---
title: "EldersAIR Health History Summary"
author: "Ethan Walker"
date: "Started 11 March 2020, Updated 12 March 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r}
# Load data

elders_ids_linked <- read_rds("Output/elders_ids_linked.rds") %>% 
  filter(winter_id == 1 | winter_id == 2) %>% 
  arrange(area, adult_id_num)

@@

# Health history summary plots
```{r, fig.height=24, fig.width=12}
health_hx_plot <- elders_health_hx %>% 
  filter(winter_id == 1) %>% 
  select(area, rheum_arth, lupus, scleroderma, psoriasis, asthma, eczema, emphysema,
         chronicbronchitis, copd, sarcoidosis, hayfever, allergies, gerd, chrohns,
         colitis, sleepapnea, kidneyfailure, pleuraleffusion, pleurisy, pneumonia,
         pneumothorax, empyema, brokenribs, coronaryarterydisease, angina, 
         heartattack, chf, abnormalhr, pacemaker, icd, valvedisease, hypertension,
         circlegs, circhead, stroke, diabetes, thyroiddisease, anemia, cancer,
         tobusenow, tobuseever, cigarspipes) %>% 
  pivot_longer(cols = c("rheum_arth":"cigarspipes"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  mutate(value = factor(value, levels = c("No", "Yes", "Not Sure", "Refused"))) %>% 
  ggplot() +
    geom_bar(aes(value, fill = area)) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    #labs(title = title_label) +
    #ylab(y_label) +
    scale_fill_manual(values = jv_palette) +
    facet_wrap(~var, ncol = 4)
health_hx_plot
```

```{r}
# Health history summary stats function

health_hx_function <- function(data, var, title_label, y_label) {

  health_hx_plot <- data %>% 
  filter(winter_id == 1) %>% 
  select(area, var) %>% 
  rename(plot_var = var) %>% 
  filter(!is.na(plot_var)) %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    labs(title = title_label) +
    ylab(y_label) +
    scale_fill_manual(values = jv_palette)
  health_hx_plot

@@

health_hx_function(elders_health_hx, "rheum_arth", "Rheumatoid Arth", "count")
health_hx_function(elders_health_hx, "lupus", "Lupus", "count")
health_hx_function(elders_health_hx, "scleroderma", "Scleroderma", "count")
health_hx_function(elders_health_hx, "psoriasis", "Psoriasis", "count")
health_hx_function(elders_health_hx, "asthma", "Asthma", "count")
health_hx_function(elders_health_hx, "eczema", "Eczema", "count")
health_hx_function(elders_health_hx, "emphysema", "Emphysema", "count")
health_hx_function(elders_health_hx, "chronicbronchitis", "Chronic bronchitis", "count")
health_hx_function(elders_health_hx, "copd", "COPD", "count")
health_hx_function(elders_health_hx, "sarcoidosis", "Sarcoidosis", "count")
health_hx_function(elders_health_hx, "hayfever", "Hayfever", "count")
health_hx_function(elders_health_hx, "allergies", "Allergies", "count")
health_hx_function(elders_health_hx, "gerd", "GERD", "count")
health_hx_function(elders_health_hx, "chrohns", "Chrohns", "count")
health_hx_function(elders_health_hx, "colitis", "Colitis", "count")
health_hx_function(elders_health_hx, "sleepapnea", "Sleep apnea", "count")
health_hx_function(elders_health_hx, "kidneyfailure", "Kidney failure", "count")
health_hx_function(elders_health_hx, "pleuraleffusion", "Pleural effusion", "count")
health_hx_function(elders_health_hx, "pleurisy", "Pleurisy", "count")
health_hx_function(elders_health_hx, "pneumonia", "Pneumonia", "count")
health_hx_function(elders_health_hx, "pneumothorax", "Pneumothorax", "count")
health_hx_function(elders_health_hx, "empyema", "Empyema", "count")
health_hx_function(elders_health_hx, "brokenribs", "Broken ribs", "count")
health_hx_function(elders_health_hx, "coronaryarterydisease", "Coronary artery disease", "count")
health_hx_function(elders_health_hx, "angina", "Angina", "count")
health_hx_function(elders_health_hx, "heartattack", "Heart attack", "count")
health_hx_function(elders_health_hx, "chf", "CHF", "count")
health_hx_function(elders_health_hx, "abnormalhr", "Abnormal HR", "count")
health_hx_function(elders_health_hx, "pacemaker", "Pacemaker", "count")
health_hx_function(elders_health_hx, "icd", "Cardiac defibrillator", "count")
health_hx_function(elders_health_hx, "valvedisease", "Valve disease", "count")
health_hx_function(elders_health_hx, "hypertension", "Hypertension", "count")
health_hx_function(elders_health_hx, "circlegs", "Circulation problems in legs", "count")
health_hx_function(elders_health_hx, "circhead", "Circulation problems in head/neck", "count")
health_hx_function(elders_health_hx, "stroke", "Stroke", "count")
health_hx_function(elders_health_hx, "diabetes", "Diabetes", "count")
health_hx_function(elders_health_hx, "thyroiddisease", "Thyroid disease", "count")
health_hx_function(elders_health_hx, "anemia", "Anemia", "count")
health_hx_function(elders_health_hx, "cancer", "Cancer", "count")
health_hx_function(elders_health_hx, "tobusenow", "Tobacco use now", "count")
health_hx_function(elders_health_hx, "tobuseever", "Tobacco use ever", "count")
health_hx_function(elders_health_hx, "agefirst", "Age started smoking", "count")
health_hx_function(elders_health_hx, "agequit", "Age quit smoking", "count")
health_hx_function(elders_health_hx, "nowperday", "cigarettes per day now", "count")
health_hx_function(elders_health_hx, "aveperday", "Average smoked per day", "count")
health_hx_function(elders_health_hx, "peakperday", "Peak smoked per day", "count")
health_hx_function(elders_health_hx, "cigarspipes", "Current/past cigar/pipe use", "count")
```

```{r}
# Health extra summary stats

health_hx_function <- function(data, var, title_label, y_label) {

  health_hx_plot <- data %>% 
  filter(winter_id == 1) %>% 
  select(area, var) %>% 
  rename(plot_var = var) %>% 
  filter(!is.na(plot_var)) %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    labs(title = title_label) +
    ylab(y_label) +
    scale_fill_manual(values = jv_palette)
  health_hx_plot

### 2020-03-12 home_char_act_summary.Rmd
plot and summary updates

---
title: "Elders home characteristics/activity summary"
author: "Ethan Walker"
date: "Started 5 March 2020, Updated 10 March 2020"
output:
  pdf_document: default
  word_document: default
---

@@

# Summary data for home characteristics
```{r}
# Summarize numeric vars: home_sqft, home_year_built, home_bedrooms, home_windows,
# home_pets, home_furry, wood_cords
home_char_summary <- home_char_clean %>% 
  filter(winter_id == 1) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  #group_by(area) %>% 
  summarize("N" = n(),
            "Mean" = mean(wood_cords, na.rm = TRUE), 
            "SD" = sd(wood_cords, na.rm = TRUE), 
            "Min" = min(wood_cords, na.rm = TRUE), 
            "Median" = median(wood_cords, na.rm = TRUE), 
            "Max" = max(wood_cords, na.rm = TRUE))
kable(home_char_summary, digits = 1, align = "c")

@@

# Summary data for home activity
```{r}
# Summarize factor vars
## Use this as a quick look at all vars
table_list <- home_act_clean %>% 
  filter(winter_id == 1) %>% 
  select(area, home_act_elect, home_act_gas, home_act_oil, home_act_other,
         home_act_propane, home_act_smoking, home_act_incense, home_act_candle,
         home_act_kerosene, home_act_windows, home_act_door, home_act_sweep) 
  #lapply(table_list, table)

@@

# Home activity summary plots
```{r}
home_act_function <- function(data, variable) {

@@

#### Abstract/manuscript tables ####

# Filter for homes that have PM data
```{r}
# 93 Winter 1 placebo homes have PM data
pm_homes_placebo <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home) %>% 
  ungroup() %>% 
  arrange(area, home)

home_char_filtered <- home_char_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  ungroup() %>% 
  arrange(area, home)

home_act_filtered <- home_act_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  ungroup() %>% 
  arrange(area, home)
```

# Summarize home data
```{r}
# Summarize numeric vars
kids_char <- home_char_filtered %>%  
  distinct(home, .keep_all = TRUE) %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(home_furry, na.rm = TRUE), 
            "SD" = sd(home_furry, na.rm = TRUE),
            "min" = min(home_furry, na.rm = TRUE), 
            "max" = max(home_furry, na.rm = TRUE))
kable(kids_char, digits = 1, align = "c")

home_char_filtered %>% 
  count(stove_age)

# Summarize factor vars
alaska_char <- home_act_filtered %>%  
  #distinct(home, .keep_all = TRUE) %>% 
  filter(area == "AK") %>% 
  group_by(home_act_sweep) %>% 
  #summarize(n = n(), percent = (n()/10)*100)
  summarize(n = n(), percent = (n()/60)*100)
alaska_char

navajo_char <- home_act_filtered %>%  
  #distinct(home, .keep_all = TRUE) %>% 
  filter(area == "NN") %>% 
  group_by(home_act_sweep) %>% 
  #summarize(n = n(), percent = (n()/23)*100)
  summarize(n = n(), percent = (n()/138)*100)
navajo_char

montana_char <- home_act_filtered %>%  
  #distinct(home, .keep_all = TRUE) %>% 
  filter(area == "WMT") %>% 
  group_by(home_act_sweep) %>% 
  #summarize(n = n(), percent = (n()/60)*100)
  summarize(n = n(), percent = (n()/360)*100)
montana_char

kids_char <- rbind(alaska_char, navajo_char, montana_char)
kids_char
```

>>>>

---
title: "Elders home characteristics/activity summary"
author: "Ethan Walker"
date: "Started 5 March 2020, Updated 12 March 2020"
output:
  pdf_document: default
  word_document: default
---

@@

```{r, include=FALSE}
# Summarize numeric vars: home_sqft, home_year_built, home_bedrooms, home_windows,
# home_pets, home_furry, wood_cords
home_char_summary <- home_char_clean %>% 
  filter(winter_id == 1) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  #group_by(area) %>% 
  summarize("N" = n(),
            "Mean" = mean(wood_cords, na.rm = TRUE), 
            "SD" = sd(wood_cords, na.rm = TRUE), 
            "Min" = min(wood_cords, na.rm = TRUE), 
            "Median" = median(wood_cords, na.rm = TRUE), 
            "Max" = max(wood_cords, na.rm = TRUE))
kable(home_char_summary, digits = 1, align = "c")

@@

```{r, include=FALSE}
# Summarize factor vars
## Use this as a quick look at all vars
table_list <- home_act_clean %>% 
  filter(winter_id == 1) %>% 
  select(area, home_act_elect, home_act_gas, home_act_oil, home_act_other,
         home_act_propane, home_act_smoking, home_act_incense, home_act_candle,
         home_act_kerosene, home_act_windows, home_act_door, home_act_sweep) 
  #lapply(table_list, table)

@@

# Home activity summary plots

```{r, fig.height=10, fig.width=8}
home_act_plot <- home_act_clean %>% 
  filter(winter_id == 1) %>% 
  select(area, home_act_gas, home_act_elect, home_act_propane, home_act_oil, 
         home_act_smoking, home_act_incense, home_act_candle, home_act_kerosene,
         home_act_windows, home_act_door, home_act_sweep) %>% 
  pivot_longer(cols = c("home_act_gas":"home_act_sweep"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  mutate(value = factor(value, levels = c("No", "Yes"))) %>% 
  ggplot() +
    geom_bar(aes(value, fill = area)) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          strip.text = element_text(size = 16, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    #labs(title = title_label) +
    #ylab(y_label) +
    scale_fill_manual(values = jv_palette) +
    facet_wrap(~var, ncol = 2)
home_act_plot
```

```{r}
home_act_function <- function(data, variable) {

@@
